CMSC818s: Project 3 \\ A Brief Survey of Modern Virtualization Research

### 2011-12-12 paper.tex
typos

Three years after VMWare's appearance, Denali sought to provide a virtualization
solution design with two goals in mind, scalability and security. Denali's authors
envisioned a separation between the management of physical hardware and the management
of software services, transforming how internet services could be deployed. Such a system 
would allow untrusted software to run on third party infrastructure, support the distribution 
of dynamic content in delivery systems, or provide virtual hosting infrastructure.

@@

At the high level, Denali provides an isolation kernel, a small kernel operating system, running
on top of x86 hardware. The kernel is designed to host many untrusted applications which are isolated
and require little data sharing. Denali multiplexes between the guest operating systems and isolates them
using private virtualized namespaces. Some special privileges, 
like dowloading a remote VM or loading initial disk images, are handled by a supervisor VM.
Since the x86 ISA includes instructioins whose behavior differs
in user and kernel mode, Denali provides a subset of the x86 ISA as well as two virtual instructions.
First, idle-with-timeout lets VMs halt their execution for a bounded amount of physical time or until
an interrupt arrives for the VM in return for a higher priority, 
and secondly Denali provides a virtual instruction which VMs can use to terminate.

>>>>

Three years after VMWare's appearance, Denali \cite{ref:denali} sought to provide a virtualization
solution design with two goals in mind, scalability and security. Denali's authors
envisioned a separation between the management of physical hardware and the management
of software services, transforming how internet services could be deployed. Such a system 
would allow untrusted software to run on third party infrastructure, support the distribution 
of dynamic content in delivery systems, or provide virtual hosting infrastructure.

@@

At the high level, Denali provides an isolation kernel, a small kernel operating system, running
on top of x86 hardware. The kernel is designed to host many untrusted applications which are isolated
and require little data sharing. Denali multiplexes between the guest operating systems and isolates them
using private virtualized namespaces. Some special privileges, 
like dowloading a remote VM or loading initial disk images, are handled by a supervisor VM.
Since the x86 ISA includes instructions whose behavior differs
in user and kernel mode, Denali provides a subset of the x86 ISA as well as two virtual instructions.
First, idle-with-timeout lets VMs halt their execution for a bounded amount of physical time or until
an interrupt arrives for the VM in return for a higher priority, 
and secondly Denali provides a virtual instruction which VMs can use to terminate.
